Evaluation of Types

### 2020-05-16 evaluation/R/evaluate-type-analysis.Rmd
Add macros

>>>>

monomorphic_parameter_count <-
unityped_positions %>%
mutate(polymorphic = map_lgl(kind, is_polymorphic)) %>%
filter(!polymorphic) %>%
pull(count) %>%
sum()

generate_macro("CountMonomorphicPositions", monomorphic_parameter_count, macro_filename)

generate_macro("PercMonomorphicPositions", monomorphic_parameter_count / total_parameter_count, macro_filename)

generate_macro("CountPositions", total_parameter_count, macro_filename)
